\lfcopyright

The training materials provided or developed by The Linux
Foundation in connection with the training services are
protected by copyright and other intellectual property
rights.

Open source code incorporated herein may have other
copyright holders and is used pursuant to the applicable
open source license.

The training materials are provided for individual use by
participants in the form in which they are provided. They
may not be copied, modified, distributed to non-participants
or used to provide training to others without the prior
written consent of The Linux Foundation.

No part of this publication may be reproduced, photocopied,
stored on a retrieval system, or transmitted without express
prior written consent.

Published by:

the \textbf{Linux
  Foundation}\\ http://www.linuxfoundation.org

No representations or warranties are made with respect to
the contents or use of this material, and any express or
implied warranties of merchantability or fitness for any
particular purpose or specifically disclaimed.

Although third-party application software packages may be
referenced herein, this is for demonstration purposes only
and shall not constitute an endorsement of any of these
software applications.

\textbf{Linux} is a registered trademark of Linus Torvalds.
Other trademarks within this course material are the
property of their respective owners.

If there are any questions about proper and fair use of the
material herein, please contact: \newline
\textbf{training@linuxfoundation.org}



